\prefacesection{Acknowledgements}
If this dissertation was 100 times longer, I still would not be able to hand out a souvenir page to all the amazing people in my life who have helped me along the way. That being said, I want to make explicit the gratitude I show to several of my friends and mentors.

To my advisor Daniel Rubin, you have been exactly everything I needed to do this work. You gave me enough freedom to grow as a research on my own while still providing enough guidance such that I didn't get lost in the purgatory of aimless projects. Whatever skills and success I have as a scientist are due in large part to how you showed me how to think.

To my committee members Ross Shachter, Mark Musen, and Curt Langlotz, thank you for the extremely entertaining and enlightening conversations. Ross, you challenged me like no other and always caught my mistakes in reasoning. It has made your approval so much more worthwhile. Mark, I would often find myself floating around MSOB looking to talk shop, and you would always indulge me if you had the time. It was always worth stopping by to talk about research and life in general. Curt, I am pretty annoyed you took so long to come to Stanford given how helpful you have been to me in the past year and half. I don't think I could ever approach being as smart as you, but I'll sure as hell try.

To BMI faculty and staff, you made the program feel more like a family than graduate school. Thank you MaryJeanne Oliva, Nancy Lennartson, John DiMario, Russ Altman, Nigam Shah, Dennis Wall, and David Paik. Stanford seemed like an intimidated place to go to graduate school until I met you all and felt welcomed.

To the Bankiewicz lab, especially Krys, John, Piotr, Mishek, and old Francisco. You taught me that research was my calling and were one of the biggest influences on my future. Thanks for taking a chance on my 20 year old self however annoying I may have been.

To my outstanding high school teachers, you taught me to love learning. Mr. Tastor, Mr. Fisher, Mrs. Kars, Mr. Westberg, whatever seed you planted in me remained today (for better or for worse).

To my BMI colleagues, you have been the best peers, friends, therapists, and guardians. Brian you were a great roommate, friend, and surfing buddy and are likely one of the funniest people I know. Jonathan, I thought you were extremely weird when I first met you, and I haven't really changed my mind about that, but you have come to be such a wonderful partner in crime. Beth, it has been a pleasure learning about life with you on our frequent coffees and beers. Katie, you always keep me on a tight leash, but you are easily the most dependable friend anybody could have. Diego, thanks for being my video game sherpa and carrying so hard. Pablo, we formed a Latino czar dream team that will never be beaten. Moskowitz, your love of food and sense of humor pretty much means I will always make time to hang out with you. Dpoz, you are easily one of the most dedicated and honest people I know, and I will always secretly try emulate that. Sarah, thank you so much for being an acceptor of all things weird; I wish you stayed around us a little longer. There are likely a lot of you I missed, take this section as an opportunity to call me out on it and I'll buy you a beer.

To Mom, Dad, Alfredo, Ari, and Lisa, you are the best family I could have. I know no better times than spending time with you all, and hard times have been a breeze knowing you were there for me. I am forever indebted and hope I give you a fraction of the support, joy, comfort, and love you have given me.

Finally, I would like to thank my funding sources the National Library of Medicine Training Grant (LM007033) and the National Institutes of Health for my Ruth L. Kirchstein National Research Service Award Fellowship (1F31CA171789-01A1 ). 